---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# argos

<!-- badges: start -->
<!-- badges: end -->

The goal of `argos` is to wrap the [`argostranslate`](https://github.com/argosopentech/argos-translate) Python module.

## Installation

You can install the development version of `argos` like so:

``` r
remotes::install_github("muschellij2/argos")
```

### Installation of `argostranslate` Python Module

To install `argostranslate`, you can either run `install_argos`, which calls `reticulate::py_install()`,  If you already have a `conda` environment enacted, use `reticulate::py_install` or simply `install_argos`

``` r
library(argos)
install_argos()
```

Or you can run `create_argos_condaenv()`, which calls `reticulate::conda_create()` and creates a conda environment for `argos`, named
`argos`.

``` r
create_argos_condaenv()
```

If you use this method, you should run `reticulate::use_condaenv("argos")` before enabling Python.


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(argos)
argos_translate("Hello World!")
```


## License
Argos Translate is dual licensed under either the [MIT License](https://github.com/muschellij2/argos/blob/master/LICENSE).
